Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})

### 2014-05-16 manuscript.tex
additional edits, .bst file created for AJB

\documentclass[12pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
%\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage{subscript}
\renewcommand{\baselinestretch}{1.5}
\bibliographystyle{apalike}

@@

\jri{Check citation format for AJB. I don't think it's numbers. adjust bibliography style accordingly } \lev{I would rather send to an open access journal. I don't like that no everyone would be able to have access to paper} \jri{AJB allows open access for \$500 which is cheaper than PLoS ONE}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
%\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage{subscript}
\renewcommand{\baselinestretch}{1.5}
\bibliographystyle{AJB}

@@

\jri{Check citation format for AJB. I don't think it's numbers. adjust bibliography style accordingly } \lev{I would rather send to an open access journal. I don't like that no everyone would be able to have access to paper} \jri{AJB allows open access for \$500 which is cheaper than PLoS ONE} \mbh{I created a .bst file for AJB...still some problems with references in bibtex file that need to be fixed}
